%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://hashbrowns.dev/}{\Large Jordi Figueras}} & Email : \href{mailto:jordi@hashbrowns.dev}{jordi@hashbrowns.dev}\\
  \href{http://hashbrowns.dev}{http://www.hashbrowns.dev} & Mobile : \href{tel:+15046173006}{+1-504-617-3006} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tulane University}{New Orleans, LA}
      {Master of Business Admininstration;  GPA: 3.51}{Aug. 2010 -- May. 2012}
    \resumeSubheading
      {Universitat Politecnica de Catalunya}{Barcelona, Spain}
      {Bachelor of Engineering in Electrical and Electronics;  }{Sep. 1999 -- Feb. 2004}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mintknight}{Remote}
      {Software Engineer - NodeJs, Solidity, React, MongoDb }{Sep 2021 - Present}
      \resumeItemListStart
        \resumeItem{API}
          {Developed REST API endpoints using Node.js, Express and MongoDB to facilitate communication between the client and the server. Utilized authentication tokens to secure API requests. Developed API documentation with Swagger for easier integration of third-party services. Implemented automated test}
        \resumeItem{Front end }
          {Developed a React-based web application using React, Redux, and TypeScript. Implemented reusable components using React and Redux to improve code maintainability and scalability. Utilized React hooks for state management and lifecycle methods in components.}
        \resumeItem{CLI}
          {Implemented new functionality to our client at the same  time we developed the API.}  
        \resumeItem{Documentation}
          {Documented our API endpoint using Swagger and Gitbook. Created a public collection on Postman }  
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Insanitea Kombucha}{New Orleans, LA}
      {Owner and Founder}{Feb 2017 - Sep 2021}
      \resumeItemListStart
        \resumeItem{Operations}
          {Designed and built Insanitea Kombucha Brand and Brewery space; Developed HACCP plans and register facility with FDA} {Became one of only two FDA approved kombucha breweries in Louisiana} {Raised seed Money}
        \resumeItem{Marketing}
          {Developed a Marketing plan with trimestral budgets; Established a sample routine with our partner retailers;} {Designed and created Brand apparel }
        \resumeItem{Sales}
          {Opened over 50 accounts in New Orleans area; Forged a relationship with a distributor in Baton Rouge; }{Opened an online e-commerce store}        
      \resumeItemListEnd

    \resumeSubheading
      {Search Influence}{New Orleans, La}
      {Ruby on rails Software Engineer}{May 2016 - Feb 2017}
      \resumeItemListStart
        \resumeItem{Ohm}
          {Developed and maintained applications using Ruby on Rails and PostgreSQL. Implemented MVC design pattern to develop web applications. Utilized JavaScript, HTML, CSS, Bootstrap and jQuery for front-end development. Used an Agile development processes and Scrum methodology}
                 
      \resumeItemListEnd

    \resumeSubheading
      {Tenbo Air}{New Orleans, LA}
      { Junior Software Engineer - Ruby on rails, Postgres, Heroku }{Sep 2014 - May 2016}
      \resumeItemListStart
        \resumeItem{Client Portal}
          {Developed and implemented Tenbo Air User platform using Ruby on Rails. Platform enabled customers to schedule services and receive electronic deliverables. Some examples of our deliverables were orthoMosaic pictures, 3D models, pdf reports }
        \resumeItem{ Product Owner}
          {Developed visual road maps to plan future services offered by Tenbo Air, defining and prioritizing customer requirements to ensure product meets customer needs and expectations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Volunteer Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{GirlsRockCamp}
      {Developed website for Summer Rock Camp Nola. SRCN brings together girls, transgender, and gender non-conforming youth ages 9-15 to learn to play an instrument, attend cool workshops https://girlsrockneworleans.org/}
    \resumeSubItem{How to use the abortion Pill}
      {Developed website for HTUAP. A Multi-language resource to learn utter information about at home abortion, the non-surgical abortion process. We provide abortion pill information to those who can take abortion pill https://www.howtouseabortionpill.org/}
%    \resumeSubItem{Nola Mesh}
%      {Attended and collaborated with this local meetup, creating a new WIFI network around the city}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			\textbf{Languages}{: JavaScript, C++, Solidity, Ruby, SQL, HTML/CSS} \\
			\textbf{Developer Tools}{: VS Code, Hardhat, Truffle, Ganache, AWS} \\
			\textbf{Technologies/Frameworks}{: Linux, nodeJs, express, React, Redux, rails, GitHub, WordPress} \\
	}}
\end{itemize}
\vspace{-16pt}

%-------------------------------------------
\end{document}
